Mendelian randomization for causal inference in Genome-wide association studies

### 2022-01-28 mr-review.Rmd
added more text

@@

Horizontal pleiotropy refers to...

@@

# Applications and Recent Findings

@@

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. To accommodate the possibility
that a trait is influenced by many genome-wide small effects,

>>>>

Recognition of complex traits' diverse genetic architectures has fueled development of MR methods with multiple instruments.

@@

Horizontal pleiotropy refers to

@@

# Recent Findings

@@

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. To accommodate the possibility
that a trait is influenced by many genome-wide, small effects,

## Multiple outcomes in MR

Investigators have found that combining information from multiple  related traits can lead to more informative MR results.

One approach to combining information across traits is to extend the univariate MR statistical methods to their multivariate analogs.

# Applications of MR in GWAS
